Introducing statistics with `intRo`

### 2016-01-20 jcgs-paper-2016/paper.Rmd
Remove unneeded text about module customization

As an example of possible customization, an instructor may wish to introduce hypothesis testing from a nonparametric framework rather than distributional. In this case, a wilcoxon rank sum test could be added easily as a module to be used instead of the T test. This addition would be fairly simple to complete. The user would fork \texttt{intRo} from http://github.com/gammarama/intRo and begin by adding six types of files to a folder within a module folder: `helper.R`, `libraries.R`, `observe.R`, `output.R`, `reactive.R`, and `ui.R`. Each of these files is written to comply with the reactive nature available in a \texttt{Shiny} application. The `ui.R` file contains all the user interface elements within the new module's tab. This will include any options in the options panel as well as results. The `helper.R` and `static.R` files refer to static functions and global variable that may be used within the module. The file `output.R` contains the reactive elements that tie output to the user interface within \texttt{Shiny} and `observe.R` and `reactive.R` contain elements within an `observer` function or `reactive` function within the \texttt{Shiny} framework. By placing each of these files within the `modules/nonparametric_test` folder and adding a single line to a navigation file indicating under which module grouping the non-parametric test module should go, a new module is available within \texttt{intRo} upon running the application. Further details on the creation of new modules can be found in section \ref{modules}.

>>>>

As an example of possible customization, an instructor may wish to introduce hypothesis testing from a nonparametric framework rather than distributional. In this case, a wilcoxon rank sum test could be added easily as a module to be used instead of the T test. This addition would be fairly simple to complete. The user would fork \texttt{intRo} from http://github.com/gammarama/intRo and begin by adding six types of files to a folder within a module folder: `helper.R`, `libraries.R`, `observe.R`, `output.R`, `reactive.R`, and `ui.R`. Each of these files is written to comply with the reactive nature available in a \texttt{Shiny} application. Further details on the creation of new modules can be found in section \ref{modules}.
